% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage{fancyhdr}

\begin{document}

\pagestyle{empty}
\renewcommand{\headrulewidth}{0.0pt}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{\sl Last updated May 11, 2012}
\name{Ahmed Mounir Gad}
\address{1600 Amphitheater pkwy \\ Mountain View, CA 94043 \\ +1 (425) 351-8760 \\ amounir@google.com}

\begin{resume}

\section{Objective}

Looking for a Software Engineer position which will help me improve my technical skills and use my expertises to contribute to
the bottom-line of my company.
 
\section{Education}

    {\sl MSc.}, Computer Vision and Artificial Intelligence \hfill Jul (2010) \\
    Universitat Autonoma de Barcelona, Spain \hspace{0.2in}  Grade: Distinction \\
    {\sl Thesis title:} Object Localization enhancement by multiple segmentations fusion

    {\sl BSc.}, Computer and Systems Engineering \hfill Jul (2008) \\
    University of Alexandria, Egypt \hspace{0.2in}  Grade: Very Good \\
    {\sl Graduation project title:} 3D Model reconstruction from an uncalibrated stereo pair of images
 
\section{Experience}
   \vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Engineer}\>{\bf Google Inc.}\> \hfill Apr (2012) - Present\\
                                    \>Mountain View, CA, USA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Joined the Geo team. Working in {\sl Google Maps} on enhancing the 45 degrees images in the imagery pipeline team.\\
    {\sl Technologies used:} Python, C++, Java, and Internal Google technologies.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Development Engineer}\>{\bf Microsoft corp.}\> \hfill Jan (2011) - Mar (2012)\\
                                    \>Bellevue, WA, USA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Joined the Online Services Division. Worked on Bing Mobile with the platforms team.
    My team was responsible for enlightening Bing experience on the Mobile phones making use of the mobile specific information like
    Location, Carrier, and Device type, etc.\\
    {\sl Technologies used:} C\#, Javascript, Web debugging tools, Web services, and Internal Microsoft technologies.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Engineer - Intern}\>{\bf Google Inc.}\> \hfill Jul (2010) - Oct (2010)\\
                                    \>Mountain View, CA, USA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Joined the Geo team. Worked on {\sl Google Earth} with the 3D reconstruction team.
    Mainly provided tools and solutions that help in getting enhanced terrain data from stereo images.\\
    {\sl Technologies used:} Java, C++, and Internal Google technologies.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Engineer - Intern}\>{\bf Google Inc.}\> \hfill Apr (2009) - Jul (2009)\\
                                    \>Mountain View, CA, USA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Joined the MENA team. The team is working on projects for (Middle East and North Africa). Examples of
    the MENA team's applications are Google {\sl Ta3reeb} and Google {\sl Ejabat}. Worked in a yet unreleased
    Google project for 80\% of the time. Built the whole infrastructure of that project. Also worked
    in {\sl Ta3reeb} and the Arabic version of {\sl news} for 20\% of the time.\\
    {\sl Technologies used:} C++, Java, Python, and Internal Google technologies.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Engineer}\>{\bf Bibliotheca Alexandrina}\> \hfill Jul (2008) - Mar (2009)\\
                           \>Alexandria, Egypt
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Joined the DAR (Digital Assets Repository) team. Our team Built the NEMO Project. NEMO is the infrastructure
    of the whole library managing the library's users’ PCs (Desktop Interface) and the librarians
    PCs (Web Interface) as well as the Multimedia library tools. I was responsible for building the client's interface
    providing functionalities like web browsing, rich text editing, sending emails with attachments, playing media,
    and managing a secure folder for each user to the library. These functionalities were provided in a secure {\sl Kiosk}
    interface that prevents the user from messing with the existing resources of the library.\\
    {\sl Technologies used:} C\#, Java, HTML, and Javascript.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Engineer - Intern}\>{\bf ITWORX}\> \hfill Jun (2007) - Aug (2007)\\
                                    \>Alexandria, Egypt
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Worked in a DB migration tool to migrate data from an Oracle to a MySQL DB. Switched to work in the DU
    account \url{http://selfcare.du.ae/}. Worked on activating the services on the Blackberry using
    the DU infrastructure.\\
    {\sl Technologies used:} Java, J2EE, and Javascript

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.3in}\= \kill % set up two tab positions
    {\bf Software Engineer - Intern}\>{\bf GPSExperts}\> \hfill Aug (2007) - Sep (2007)\\
                                    \>Alexandria, Egypt
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Worked on a tool for image processing functionalities. The tool was capable of doing some basic image processing tasks like
    zooming, smoothing, and edge detection.\\
    {\sl Technologies used:} C++ MFC.

\section{Skills}
    {\bf Software Design}\\
    Very good knowledge about UML diagrams and design patterns.

    {\bf Desktop Development}\\
    Excellent in programming using C, C++, Java, Python and C\#\\
    Good knowledge of prototyping using Matlab.

    {\bf Web Development}\\
    Good knowledge of HTML, CSS, Javascript, jQuery, Django and Java EE.

    {\bf Database Development}\\
    Knowledge of DBMSs like MySQL, Oracle and Microsoft SQL Server.\\
 
\section{Grants and Scholarships}

Awarded the PIFF grant offered by the Spanish Ministry of Education and Science and the Catalan Government for the purpose of continuing a
MSc. and PhD program, July 2009.

\section{Honors and Awards}
    \begin{itemize}
    \item Egyptian Mathematical Olympiad (EMO) 2003, Gold Medal.
    \item Egyptian Olympiad of Informatics (EOI) 2006, Silver Medal.
    \item Egyptian National ICPC 2006, 10th place.
    \item Arab and North-Africa regional ICPC 2006, 4th place “First participation for Alex. University”.
    \item Al-Akhawain University in Ifrane (AUI) TopCoder contest, WINNER.
    \item GUC National Warm-up contest for the ICPC 2007, 4th place.
    \item Arab and North Africa regional ICPC 2008 7th place.
    \end{itemize}
 
\section{Activities}          
    \begin{itemize}
    \item Participate regularly in online programming competitions on USACO, COCI, SPOJ, ACM UVA, ACM PKU, ACM TJU and almost weekly SRMs on TopCoder.com.
    \item Organized a local ACM-like contest in Alexandria University, problem setter and the judge.
    \item Ex-Member of the Interact club Pharos ``Rotary''.
    \item Ex-Member in the Egyptian Parachuting team ``4th place in 2003''.
    \end{itemize}

\section {References}
% \vspace{-0.1in}
% \begin{tabbing}
%  \hspace{2.75in}\=\kill
% {\bf Mohamed G. Elfeky}    \> {\bf Tilman Reinhardt}             \\
% Software Engineer - Google \> Member of technical staff - Google \\
% mgelfeky@google.com        \> tilman@google.com                  \\
% +1 (650)215-0544           \> +1 (650)214-2162                   
% \end{tabbing}
% 
% \begin{tabbing}
%  \hspace{2.75in}\=\kill
% {\bf Ramon Baldrich}      \> {\bf Youssef Mikhail Bassily}               \\
% Associate Professor - UAB \> Head of ICT Dept. - Bibliotheca Alexandrina \\
% ramon@cvc.uab.es          \> youssef.mikhail@bibalex.org                 \\
% +34 (935)81-2592          \> +(203) 483-9999, Ext: 1428                   
% \end{tabbing}
Available upon request.

\end{resume}
\end{document}